### 2022-11-29 dissertation/chapters/08-results.tex
🚧 (final-review): Chapter 8, before distribution changes
🚧 WIP

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The probabilities of the \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}

>>>>

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of \index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

\subsection{Probabilities of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probabilities of \index{heuristic}heuristic selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves. The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
            \caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
            \label{fig:results:case_study:thetas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
            \caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
            \label{fig:results:case_study:thetas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
            \caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
            \label{fig:results:case_study:thetas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
            \caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
            \label{fig:results:case_study:thetas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The probabilities of \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:thetas}
\end{figure}
